18.821 - Poker Chips Finite board configurations

### 2014-09-22 FiniteBoards.tex
modified stuff

\begin{lemma}
\label{finiteextension}
Suppose $\sum_{x,y} f(x,y) = S$, and all chips are within the range $[x_l, x_h] \times [y_l, y_h]$. Then $E^n(f)$ only contains chips within the range $[x_l - \log S, x_h + \log S] \times [y_l-\log S, y_h+\log S]$ for all $n$.
\end{lemma}

\begin{proof}
For each chip that moves in one direction, there is another chip that moves in the opposite direction. Therefore, at each time, the number of chips that extend the range can be at most half of what extended before. This means that there are at most $\log S$ extensions on each side. 
\end{proof}

>>>>

\begin{lemma}
\label{finiteextension}
Suppose $\sum_{x,y} f(x,y) = S$, and all chips are within the range $[x_l, x_h] \times [y_l, y_h]$. Then $E^n(f)$ only contains chips within the range $[x_l - \sqrt{S}, x_h + \sqrt{S}] \times [y_l-\sqrt{S}, y_h+\sqrt{S}]$ for all $n$.
\end{lemma}

\begin{proof}
Let $A$ be an initial region of the board
\end{proof}
